\LARGE \bf ***

### 2020-09-23 icra-2021.tex
Ulrik's review implemented (2)

Mission planning for unmanned aerial vehicles (UAVs) operating in outdoor scenarios such as precision agriculture, search and rescue, and surveillance is a challenging task. It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying. Currently, UAVs operating in outdoor scenarios are often semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The current state of practice in mission planning for UAVs has prompted us to proposes an \emph{energy-aware dynamic mission planning algorithm} that addresses the broader problem of increasing \emph{computational demands} and their relation to the energy consumption, path, and autonomy.

>>>>

Mission planning for unmanned aerial vehicles (UAVs) operating in outdoor scenarios such as precision agriculture, search and rescue, and surveillance is a challenging task. It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of patterns detected while flying. Currently, UAVs flying outdoors are often semi-autonomous, in the sense that the mission is static and usually defined using a mission planning software~\cite{daponte2019review}. Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs that highlights the increasing \emph{computational demands} and their relation to the energy consumption, path, and autonomy.
